### 2015-01-20 src/conclusion.Rnw
conclusion

This suggests that that none of the well known reduction strategies are
actually able to consistenly select useful mutants, and the best path forward
for a working tester is to rely on the simplest scheme of all -- the random
selection of mutants.

There is a second possible point of interest here: as with coverage
metrics used to predict mutation scores~\cite{gopinath2014code}, using
a large body of actual open source code to perform experiments seems
to favor simple and easily-implemented approaches much more strongly
than limited experiments on more academic subjects.  We speculate that
the inadequacies in real world test suites may frequently be more simply
predicted and evaluated than for typical research subjects, which may
be smaller or involve less easily distinguished test suites.

>>>>

This suggests that that none of the well known reduction strategies are
actually able to consistently select useful mutants, and the best path forward
for a working tester is to rely on the simplest scheme of all -- the random
selection of mutants.

There is a second possible point of interest here: as with coverage
metrics used to predict mutation scores~\cite{gopinath2014code}, using
a large body of actual open source code to perform experiments seems
to favor simple and easily-implemented approaches much more strongly
than limited experiments on more academic subjects.  We speculate that
the inadequacies in real world test suites may frequently be more simply
predicted and evaluated than for typical research subjects, which may
be smaller or involve less easily distinguished test suites.
% TODO: Should we add this.
%\begin{comment}

There is also an inherent danger to using only a small sample of same academic
subjects over and over again. We may tend to see patterns that are specific
to the subjects, which are not present in the wider population. The
non-performance of the popular strategies against a wider dataset such as
ours may also be seen as a possible symptom of this over-fitting.
%\end{comment}
